JavaScript as an Embedded DSL

### 2012-03-29 papers/ecoop2012/article.tex
minor grammar

Also, we integrated our DSL with an existing web framework, Play 2.0.\footnote{\url{http://www.playframework.org}}
Our DSL can be used to define Play form validators that are executed both at the client and the server side.
We managed to achieve that without deep changes to how the framework works internally proving that our
DSL can be used as a library.

>>>>

Also, we integrated our DSL with an existing web framework, Play 2.0.\footnote{\url{http://www.playframework.org}}
Our DSL can be used to define Play form validators that are executed on both the client and server sides.
We managed to achieve that without deep changes to how the framework works internally proving that our
DSL can be used as a library.
